Perturbation theory in the complex plane: Exceptional points and where to find them

### 2020-11-13 Manuscript/EPAWTFT.tex

%===============================%
\subsection{Cases of divergence}
%===============================%

>>>>

Recently, Mih\'alka \textit{et al.} studied the partitioning effect on the convergence properties of Rayleigh-Schr\"odinger perturbation theory by considering the MP and the EN partitioning as well as an alternative partitioning. \cite{Mihalka_2017a} 
Taking as an example (in particular) the water molecule at equilibrium and at stretched geometries, they could estimate the radius of the convergence via a quadratic Pad\'e approximant and convert divergent perturbation expansions to convergent ones in some cases thanks to a judicious choice of the level shift parameter.
In a subsequent study by the same group, \cite{Mihalka_2017b} they use analytic continuation techniques to resum divergent series taking again as an example the water molecule in a stretched geometry.
In a nutshell, their idea consists in calculating the energy of the system for several values of $\lambda$ for which the MP series is rapidly convergent, and to extrapolate the final energy to the physical system at $\lambda = 1$ via a polynomial- or Pad\'e-based fit. 
However, the choice of the functional form of the fit remains a subtle task.
This technique was first generalized by using complex scaling parameters and applying analytic continuation by solving the Laplace equation, \cite{Surjan_2018} and then further improved thanks to Cauchy's integral formula
\begin{equation}
	\frac{1}{2\pi i} \oint \frac{E(z)}{z - a} = E(a)
\end{equation}
instead of the solution of the Laplace equation. \cite{Mihalka_2019}

%==========================================%
\subsection{Insights from a two-state model}
%==========================================%
